---
title: "Christopher Lewis's CV"
author: Christopher Lewis
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/14NWLBFWAsw34Ffb50Qk9urG8jUzGNPVwkCPKbALpd3w/edit?usp=sharing",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================
<!--
```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
datadrivencv::build_network_logo(CV$entries_data)
```
-->

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```

Skills {#skills}
--------------------------------------------------------------------------------

- <i class="fa fa-laptop"></i> **Programming**: R, SQL, Python, HTML, CSS, Git
<!--
- <i class="fa fa-flask"></i> **Laboratory**: DOE, Flow Testing, Rheology, UV/VIS spectroscopy, basic lab equipment (pH, separation methods, condensers) -->
- <i class="fa fa-lightbulb-o"></i> **Other**: data analysis, data visualization, statistics, experimental design, science writing

Online Courses
--------------------------------------------------------------------------------

- **Coursera**: Python for Everybody, UMich;
<!--
Credentials
--------------------------------------------------------------------------------
-->

<br>
<br>
<br>
<br>
<br>
<br>

```{r}
if(params$pdf_mode){
  cat("View this CV online with links at _christopherlewis.me/cv/_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/ChrLew/cv/blob/main/Lewis_cv.pdf)")
}
```

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

The source code is available [on github.com/ChrLew/cv](https://github.com/ChrLew/cv).

Last updated on `r Sys.Date()`.

Main
================================================================================

Christopher Lewis {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('education')
```

Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('industry_positions')
```


```{css, echo=FALSE}
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```

Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('research_positions')
```

Publications {data-icon=book}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```

Patents {data-icon=award}
--------------------------------------------------------------------------------
```{r}
CV %<>% print_section('patents')
```
